Towards a miniKanren with fair search strategies

### 2019-05-27 Paper/paper.tex
cite DFSi uKanren
cite boskin

miniKanren is a family of relational programming languages.
\citet{Friedman:2005:RS:1121583,friedman_reasoned_2018} introduce
miniKanren and its implementation in \emph{The Reasoned Schemer} 
and \emph{The Reasoned Schemer, 2nd Ed} (TRS2). Although originally written in 
Scheme, miniKanren has been implemented in many other languages, including
multiple ones using the same language. (See miniKanren.org.) This has come
about because of Hemann et al.'s work on microKanren. Also, miniKanren
has been ported to Ocaml, and named OCanren\citep{kosarev2018typed}). 
\citet{byrd2017unified} have 
demonstrated that miniKanren problems that at first reading seem impossible
are indeed possible by using a Scheme interpreter written in miniKanren, thereby
having access to logic variables within Scheme.
miniKanren.org contains the seeds of many interesting problems and 
their solutions.

\NOTE[DPF]{I thought we agreed to use BFSser throughout?  
In that sense it had emerged a few days ago, and now it has
re-emerged.  It is what we are going to use instead of ``current''.}

@@

\DFSi{} is not always the best choice. For instance, it might be less 
desirable for novice miniKanren users---understanding implementation details 
and fiddling with clause order is not their first priority. 
There is another reason that miniKanren could use more search strategies than
just \DFSi. In many applications, there does not exist one order that serves all
purposes. For example, a relational dependent type checker contains
clauses for constructors that build data and clauses for eliminators that use
data. When the type checker is generating simple and shallow programs,
the clauses for constructors had better be at the top of the
\conde{} expression.
When performing proof searches for complicated programs, the clauses for 
eliminators had better be at the top of the \conde{} expression. With \DFSi, 
these two uses cannot be efficient at the same time. In fact, to make one use 
efficient, the other one must be more sluggish.

>>>>

miniKanren is a family of relational programming languages.
\citet{Friedman:2005:RS:1121583,friedman_reasoned_2018} introduce
miniKanren and its implementation in \emph{The Reasoned Schemer} 
and \emph{The Reasoned Schemer, 2nd Ed} (TRS2). Although originally written in 
Scheme, miniKanren has been implemented in many other languages, including
multiple ones using the same language. (See miniKanren.org.) This has come
about because of \citet{Hemann_2016}'s work on microKanren, a core of 
miniKanren comprised of only 54 LOC. Also, miniKanren
has been ported to Ocaml, and named OCanren\citep{kosarev2018typed}). 
\citet{byrd2017unified} have 
demonstrated that miniKanren problems that at first reading seem impossible
are indeed possible by using a Scheme interpreter written in miniKanren, thereby
having access to logic variables within Scheme.
miniKanren.org contains the seeds of many interesting problems and 
their solutions.

\NOTE[DPF]{I thought we agreed to use BFSser throughout?  
In that sense it had emerged a few days ago, and now it has
re-emerged.  It is what we are going to use instead of ``current''.}
\NOTE[LKC]{}

@@

\DFSi{} is not always the best choice. For instance, it might be less 
desirable for novice miniKanren users---understanding implementation details 
and fiddling with clause order is not their first priority. 
There is another reason that miniKanren could use more search strategies than
just \DFSi. In many applications, there does not exist one order that serves all
purposes. For example, a relational dependent type checker contains
clauses for constructors that build data and clauses for eliminators that use
data. When the type checker is generating simple and shallow programs,
the clauses for constructors had better be at the top of the
\conde{} expression.
When performing proof searches for complicated programs, the clauses for 
eliminators had better be at the top of the \conde{} expression. With \DFSi, 
these two uses cannot be efficient at the same time. In fact, to make one use 
efficient, the other one must be more sluggish. \citet{boskin} propose and 
implement a means to eliminate or re-order disjunctive clauses to accommodate 
varying search needs such as these.

\NOTE[LKC]{I have cited Boskin in the above paragraph.}
